---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# `tidyquandl`

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/ClaytonJY/tidyquandl.svg?branch=master)](https://travis-ci.org/ClaytonJY/tidyquandl)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/ClaytonJY/tidyquandl?branch=master&svg=true)](https://ci.appveyor.com/project/ClaytonJY/tidyquandl)
[![Coverage status](https://codecov.io/gh/ClaytonJY/tidyquandl/branch/master/graph/badge.svg)](https://codecov.io/github/ClaytonJY/tidyquandl?branch=master)

The goal of `tidyquandl` is to be an easy-to-use and tidy interface to the [Quandl](https://www.quandl.com/) API for financial data.

Core features:

- focuses on the Tables API (the good one)
- returns tibbles (except for metadata)
- always fetches all results (`paginate = TRUE` in `Quandl`)
- automatically retries failed queries
- automatically splits large queries into manageable ones (batching)
- uses `readr::read_csv()` for speed and type inference

This is not the only way to interact with Quandl from R; Quandl themselves maintain a [`Quandl` R package](https://github.com/quandl/quandl-r) which covers a wider set of uses than `tidyquandl` (like the Timeseries API). An earlier version of this package wrapped the Quandl one, but as of v0.1.2 the underlying code has been rewritten from scratch.


## Installation

You can install the release and development versions from [GitHub](https://github.com/) wih the `devtools` package:

```{r installation, eval=FALSE}
# install.packages("devtools")

# latest release
devtools::install_github("claytonjy/tidyquandl@*release")

# latest development version
devtools::install_github("claytonjy/tidyquandl")
```

I recommend using the release version in general, but be sure to install the development version when filing bugs and pull requests.


## Usage

Before doing anything with the Quandl API, you'll need an account; you can register for free at [Quandl](https://www.quandl.com/), and all examples use free datasets available to all registered users.

Then you need to obtain your API key (a string) from your [account settings](https://www.quandl.com/account/api). Storing this in an environment variable named `QUANDL_API_KEY` is easiest (e.g. via `.Renviron`), though isn't strictly necessary.

```{bash, eval=FALSE}
# ~/.Renviron
QUANDL_API_KEY=my-ap1k3y
```

Then we read that in via `quandl_key_set()`.

```{r set-api-key}
library(tidyquandl)

quandl_key_set()  # can also pass key to this as argument
```

Now we can call `quandl_datatable()` to interact with the Tables API. Here we use the [Wiki Prices database](https://www.quandl.com/databases/WIKIP) to get one day of prices on Apple and Microsoft:

```{r simple-query}
quandl_datatable("WIKI/PRICES", ticker = c("AAPL", "MSFT"), date = "2018-01-02")
```

Unlike `Quandl::Quandl.datatable`, if an error is received (HTTP response 400+) the query will be retried automatically up to three times. It can also accept an unlimited number of `tickers`: behind the scenes, multiple queries will be made to avoid errors from passing Quandl too many parameters.

You can pass in any of the arguments you're used to passing into `Quandl::Quandl.datatable` via the `...` args. Here we get only the closing prices for Apple over the span of two weeks.

```{r complex-query}
quandl_datatable(
  "WIKI/PRICES",
  ticker = "AAPL",
  date.gte = "2018-01-01", date.lt = "2018-01-15",
  qopts.columns = c("ticker", "date", "close")
)
```

You can also use `tidyquandl` to fetch metadata about a table.

```{r}
quandl_datatable_meta("WIKI/PRICES")
```

Unlike `quandl_datatable()` this returns a list rather than a tibble. This can also be used on any table, including premium tables you haven't paid for, which can be helpful to evaluate their usefullness beyond what you see in the documentation.


## Roadmap

The next big changes will be to allow for more `readr`-like control of types (issues #22, #27) and to improve documentation by making a `pkgdown` site (#9) and a vignette comparing this to the `Quandl` package more directly (#28).


## Contributing

Your contributions are welcome! Issues, typo fixes, new functions, anything. See `.github/CONTRIBUTING.md` for more information.

To test & check you'll _need_ to store your key in the `QUANDL_API_KEY` variable. I recommend creating an `.Renviron` file _in this directory_.

Please note that this project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
