---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# tidyquandl

The goal of tidyquandl is to be an easier-to-use and tidy interfact to the [Quandl](https://www.quandl.com/) API for financial data.


## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ClaytonJY/tidyquandl")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tidyquandl)

quandl_api_key(Sys.getenv("QUANDL_API_KEY"))

quandl_datatable("WIKI/PRICES", ticker = "AAPL", date.gte = "2018-01-01")
```


## Contributing

Please note that this project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
